---
title: "Bcp_freq"
author: "XuranZeng"
date: "9/14/2021"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=5, fig.pash='Figs/', echo = TRUE, warning=FALSE, message=FALSE)
```

## Update:
### 9/21
1. Time series charts: add moving average lines to 
2. Heatmap of months and zones: calculate log, order by zones


```{r, echo=FALSE}
library(readr)
library(PerformanceAnalytics)
library(lubridate)
library(zoo)
library(xts)
library(ggplot2)
library(dplyr)
Bpc_freq<-read_csv("/project/graziul/data/bpc_freq.csv")
Bpc_freq$ts<-ymd_hm(unlist(Bpc_freq[,3]))
Bpc_freq<-Bpc_freq[,c(5,1,2,3,4)]
```


```{r}
#description(zone-days-start-end-files-hours of speech)
zone_list<-unique(Bpc_freq$zone)

des<-data.frame(zone=zone_list)
for (i in 1:length(zone_list)){
  des[i,"ndays"]<-nrow(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'date']))
  des[i,"start"]<-head(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'ts']),1)
  des[i,"end"]<-tail(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'ts']),1)
  des[i,"nfiles"]<-nrow(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),])
  des[i,"num_bpc"]<-sum(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),"num_bpc"])
}
print(des)
```

```{r,echo=FALSE}
zone_1<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 1"),])
zone_10<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 10"),])
zone_11<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 11"),])
zone_12<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 12"),])
zone_13<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 13"),])
zone_2<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 2"),])
zone_3<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 3"),])
zone_4<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 4"),])
zone_5<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 5"),])
zone_6<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 6"),])
zone_8<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 8"),])
```

## Visualization
```{r,echo=FALSE}
#plot
sma<-stats::filter(ts(zone_1[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_1, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("Zone_1")

sma<-stats::filter(ts(zone_2[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_2, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_2")

sma<-stats::filter(ts(zone_3[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_3, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_3")

sma<-stats::filter(ts(zone_4[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_4, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_4")

sma<-stats::filter(ts(zone_5[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_5, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_5")

sma<-stats::filter(ts(zone_6[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_6, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_6")

sma<-stats::filter(ts(zone_8[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_8, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_8")

sma<-stats::filter(ts(zone_10[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_10, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_10")

sma<-stats::filter(ts(zone_11[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_11, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_11")

sma<-stats::filter(ts(zone_12[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_12, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_12")

sma<-stats::filter(ts(zone_13[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_13, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_13")

```

```{r,echo=FALSE}
sum_by_freq<-function(data,freq){
  data %>%
    mutate(freq=freq(data$ts)) %>%
    group_by(freq) %>%
    summarise(sum_by_mon=sum(log(num_bpc)))
}

a1<-sum_by_freq(zone_1,month)
colnames(a1)<-c("month","zone_1")
a2<-sum_by_freq(zone_2,month)
colnames(a2)<-c("month","zone_2")
a3<-sum_by_freq(zone_3,month)
colnames(a3)<-c("month","zone_3")
a4<-sum_by_freq(zone_4,month)
colnames(a4)<-c("month","zone_4")
a5<-sum_by_freq(zone_5,month)
colnames(a5)<-c("month","zone_5")
a6<-sum_by_freq(zone_6,month)
colnames(a6)<-c("month","zone_6")
a8<-sum_by_freq(zone_8,month)
colnames(a8)<-c("month","zone_8")
a10<-sum_by_freq(zone_10,month)
colnames(a10)<-c("month","zone_10")
a11<-sum_by_freq(zone_11,month)
colnames(a11)<-c("month","zone_11")
a12<-sum_by_freq(zone_12,month)
colnames(a12)<-c("month","zone_12")
a13<-sum_by_freq(zone_13,month)
colnames(a13)<-c("month","zone_13")

b<-cbind(a1, a2, a4,  a8, a10, a11, a12, a13)[,c(1,2,4,6,8,10,12,14,16)]
c<-merge(b, a3, by = 'month', all=T)
d<-merge(c, a5, by = 'month', all=T)
e<-merge(d, a6, by = 'month', all=T)
g<-e[,c(1,2,3,10,4,11,12,5,6,7,8,9)]
library(reshape2)
f<-melt(g, id="month")

mymonths<-c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul","Aug","Sep","Oct","Nov","Dec")
month.name<-sort(unique(f$month))
f$month2<-factor(f$month, levels=month.name, labels=mymonths)

ggplot(data=f, aes(x=month2, y=variable))+
  theme_bw(base_family = "STKaiti")+
  geom_tile(aes(fill=value),colour="white")+
  scale_fill_gradient(low="white", high="black")+
  ggtitle("month-zone(log)")+
  xlab("month")+
  ylab("zones")



```


```{r,echo=FALSE, fig.width=12, fig.height=3}
plot_hm<-function(data){
  data$week<-week(data$ts)
  data$weekdays<-weekdays(data$ts)
  zone_hm<-ggplot(data=data, aes(x=week, y=weekdays))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=num_bpc),colour="white")+
    scale_fill_gradient(low="white", high="black")
  return(zone_hm)
}

plot_hm(zone_1[,c(1,5)])+ggtitle("zone_1")
plot_hm(zone_2[,c(1,5)])+ggtitle("zone_2")
plot_hm(zone_3[,c(1,5)])+ggtitle("zone_3")
plot_hm(zone_4[,c(1,5)])+ggtitle("zone_4")
plot_hm(zone_5[,c(1,5)])+ggtitle("zone_5")
plot_hm(zone_6[,c(1,5)])+ggtitle("zone_6")
plot_hm(zone_8[,c(1,5)])+ggtitle("zone_8")
plot_hm(zone_10[,c(1,5)])+ggtitle("zone_10")
plot_hm(zone_11[,c(1,5)])+ggtitle("zone_11")
plot_hm(zone_12[,c(1,5)])+ggtitle("zone_12")
plot_hm(zone_13[,c(1,5)])+ggtitle("zone_13")
```

## Focus on zone 1
```{r}
#plot

#ggplot(data = zone_1, aes(x=ts, y=num_bpc)) +  geom_col(position = 'dodge')+theme(axis.text.x = element_text(angle=90,hjust=1))

plot(xts(zone_1[,5],order.by=zone_1[,1]),main="zone 1")

```


### decompose-trend-seasonal-random
```{r}
library(TTR)
tss<-ts(zone_1[,5],freq=1800,start=1)
ts_components<-decompose(tss)
plot(ts_components)


ts_seasonally_adjusted<-tss-ts_components$seasonal
plot(ts_seasonally_adjusted)

```

```{r,echo=FALSE}
data<-zone_1[,c(1,5)]
ts<-xts(zone_1[,5],order.by=zone_1[,1])
```

### stationary test
```{r}
print(acf(data$num_bpc, lag.max = 20, main="auto-correlation test(20)"))
print(pacf(data$num_bpc, lag.max = 20, main="partial auto-correlation test"))
acf(data$num_bpc, lag.max = 200, main="auto-correlation test(200)")
```

#### non-stationary timeseries of seasonal-change

### kpss unit root test
```{r}

library(urca)
summary(ur.kpss(data$num_bpc))
```
#### value of test > critical value (1pt), refuse H0:stationary, =>non-stationary

### diff
```{r}
# use KPSS test to determine the appropriate number of differences
# nonstationary->stationary

library(forecast)
ndiffs(tss)
```

#### first-order difference. 

```{r}
summary(ur.kpss(diff(tss)))
```
#### differenced data are stationary. 


```{r}
tss %>% diff %>% ggtsdisplay(main="")
```

#### According to the ACF and PACF, we could set an initial candidate model ARIMA(1,0,1) or use autoarima(min AIC).

### auto-arima
```{r}
# auto-arima
ts_adj<-diff(tss)
fit<-auto.arima(ts_adj,seasonal = FALSE)
summary(fit)

```

#### This is an ARIMA(1,0,1) model.\

Y~t~ = c + 0.2041Y~t-1~ -0.6929 epsilon ~t-1~ + epsilon ~t~

```{r}
fit %>% forecast(h=10) %>% autoplot(include=80)
```

### check residuals
```{r}

checkresiduals(fit)

```

#### P-value, residuals are not white-noise, use ARCH model

```{r}
res<-fit$residuals
res2<-res^2
par(mfrow=c(1,2))
acf(as.vector(res2),main="ACF of Squared Residuals")
pacf(as.vector(res2),main="PACF of Squared Residuals")
```

#### some spikes are out of the white noise bands, i.e there is a correlation between them, that is an indication of heteroscedasticity problem and usage of ARCH-GARCH model

### Eagles ARCH test
```{r}
library(MTS)
archTest(res)
```
#### p value less than alpha, reject H0, exist ARCH effects

### GARCH
```{r}
library(rugarch)
spec = ugarchspec()
def.fit=ugarchfit(spec=spec, data=ts_adj)
print(def.fit)
```

#### 1-estimated parameters: except mu parameter, all parameters are significant\  
Y~t~ = 0.00441 + 0.82383 R~1~ + 0.57602 A~1~\
Omega^2 = 0.43604 + 0.59209(A~t-1~)^2 + 0.53307(A~t-2~)^2\

#### 2-Ljung-Box Test: residuals do not have autocorrelation\  

#### 3-ARCH LM Test: GARCH process is adequately fitted\  






