---
title: "arrest domestic descriptive analysis"
author: "XuranZeng"
date: "10/6/2021"
output: 
  html_document: 
    toc: true
    theme: united
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=3, fig.pash='Figs/', echo = TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library(readr)
#library(rmgarch,lib='~/R/x86_64-pc-linux-gnu-library/3.2/')
library(rugarch)
library(lubridate)
library(zoo)
library(xts)
library(ggplot2)
library(dplyr)
library(knitr)
library(corrplot)
library(forecast)


```

```{r,echo=FALSE}
# Input: dataframe of raw data (col:primary type, day)
# Output: dataframe (col:types, row:day)
# Functionality: transform the format of data, aggregata and sum to get daily time series of different types
trans<-function(x){
  a<-aggregate(x$`Primary Type`,by=list(day=x$day, type=x$`Primary Type`),length)
  
  type_ts2<-as.data.frame(unique(a$day))
  colnames(type_ts2)<-"day"
  for (i in 1:length(unique(a$type))){
    b<-subset(a[which(a$type==unique(a$type)[i]),])
    type_ts2<-merge(type_ts2,b[,c(1,3)],by="day",all=TRUE)
    colnames(type_ts2)[(i+1)]<-unique(a$type)[i]
  }
  
  b<-type_ts2
  rownames(b)<-b$day
  b<-b[,-1]
}
```

```{r, echo=FALSE}
# Input: time series (col: type, row:day/month/week/...)
# Output: correlation matrix
# Functionality: Compute correlation coefficient and p-value

corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                    result=c("none", "html", "latex")){
  #Compute correlation matrix
  #require(Hmisc)

  library(rstatix)
  R <- cor_mat(x) # Matrix of correlation coefficients
  p <- cor_get_pval(R) # Matrix of p-value 
  
  ## Define notions for significance levels; spacing is important.
  mystars <- ifelse(p < .0001, "****", ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    "))))
  mystars<-mystars[,-1]
  ## trunctuate the correlation matrix to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R)[,-2], 2))[,-1]
  
  ## build a new matrix that includes the correlations with their appropriate stars
  Rnew<-R
  for (i in 1:nrow(R)){
    Rnew[i,]<-paste(R[i,], mystars[i,], sep="")
  }
  
  ## remove upper triangle of correlation matrix
if(removeTriangle[1]=="upper"){
  Rnew <- as.matrix(Rnew)
  Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
  Rnew <- as.data.frame(Rnew)
}

## remove lower triangle of correlation matrix
else if(removeTriangle[1]=="lower"){
  Rnew <- as.matrix(Rnew)
  Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
  Rnew <- as.data.frame(Rnew)
}
  
  rownames(Rnew) <- colnames(x)
  return(Rnew)

}

```

# different districts

## raw frequencies
```{r, echo=FALSE, fig.height=5}
# time: entire sample
# log(num_reported_crime)
crimes_data<-read_csv("/home/xuranzeng/project/crimes_data.csv",)
crimes_data$day<-date(as.Date(unlist(crimes_data$Date),"%m/%d/%Y"))
crimes_data_sample<-crimes_data[,c(10, 3,4,8,9)]
crimes_types<-c("ASSAULT","BATTERY" , "HOMICIDE", "ROBBERY" )
```

```{r, echo=FALSE}
raw_frequency<-subset(crimes_data_sample[which(crimes_data_sample$`Primary Type`  %in% crimes_types),])
raw_frequency_plot<-aggregate(raw_frequency$`Primary Type`,by=list(district=raw_frequency$District, type=raw_frequency$`Primary Type`),length)
raw_frequency_plot$x<-log(raw_frequency_plot$x)
```

```{r, echo=FALSE}
data<-raw_frequency_plot
colnames(data)<-c("district","type","x")

ggplot(data=data, aes(x=district, y=type))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=x),colour="white")+
    geom_text(aes(label = round(x, 1)), size = 3.5) +
    scale_fill_gradient(low="white", high="steelblue")+
    ggtitle("2001-2021")+
    coord_fixed()
```

1-The districts where the police are under greatest stress are 11, 7,6,4.\
2-The districts where the police are under greatest stress are 20, 1.\
3-There exists correlation between crimes. The district with most homicide(11) also has almost most battery, assault and robbery. The district with least homicide(20) has least battery, assault, and robbery.


```{r, echo=FALSE}
b<-aggregate(raw_frequency$`Primary Type`,by=list(district=raw_frequency$District, type=raw_frequency$`Primary Type`, arrest=raw_frequency$Arrest),length)
true<-b[which(b$arrest==TRUE),]
colnames(true)<-c("district","type","arrest","true")

all<-aggregate(raw_frequency$`Primary Type`,by=list(district=raw_frequency$District, type=raw_frequency$`Primary Type`),length)
colnames(all)<-c("district","type","all")
arrest<-merge(all,true,all = TRUE)
arrest<-na.omit(arrest)
arrest$rate<-round(arrest$true/arrest$all,2)
```

## arrest reports
```{r, echo=FALSE}
arrest_reports<-arrest[,c("district","type","true")]
arrest_reports$true<-log(arrest_reports$true)
data<-arrest_reports
colnames(data)<-c("district","type","x")

ggplot(data=data, aes(x=district, y=type))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=x),colour="white")+
    geom_text(aes(label = round(x, 1)), size = 3.5) +
    scale_fill_gradient(low="white", high="steelblue")+
    ggtitle("2001-2021")+ 
    theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), panel.background = element_blank())+
    coord_fixed()
```

## arrest rates
```{r, echo=FALSE}
arrest_rate<-arrest[,c("district","type","rate")]
data<-arrest_rate
colnames(data)<-c("district","type","x")

ggplot(data=data, aes(x=district, y=type))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=x),colour="white")+
    geom_text(aes(label = round(x, 2)), size = 3.5) +
    scale_fill_gradient(low="white", high="steelblue")+
    ggtitle("2001-2021")+ 
    theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), panel.background = element_blank())+
    coord_fixed()
```

From the perspective of districts:\
1-Districts with fewer crimes reports (1,16,17,18,19,20,23) have higher arrest rates.\
2-Districts with more reports(11,7,6,4) have lower arrest rates.\
3-Does the low arrest rate mean that some reported crimes did not occur? Or it is because they actually occurred but the police failed to arrest? I do not understand the label "arrest", it is an action or a result?\
From the perspective of types:\
1-Homicide has least reports but highest arrest rates, and homicide is the type of crime which put most stress on police. Is the high arrest rate means that the police pay most attention on it? They work best under greatest stress? \

## domestic reports
```{r, echo=FALSE}
b<-aggregate(raw_frequency$`Primary Type`,by=list(district=raw_frequency$District, type=raw_frequency$`Primary Type`, Domestic=raw_frequency$Domestic),length)
true<-b[which(b$Domestic==TRUE),]
colnames(true)<-c("district","type","Domestic","true")

Domestic<-merge(all,true,all = TRUE)
Domestic<-na.omit(Domestic)
Domestic$rate<-round(Domestic$true/Domestic$all,2)
  
Domestic_rate<-Domestic[,c("district","type","rate")]
```

```{r, echo=FALSE}
Domestic_reports<-arrest[,c("district","type","true")]
Domestic_reports$true<-log(Domestic_reports$true)
data<-Domestic_reports
colnames(data)<-c("district","type","x")

ggplot(data=data, aes(x=district, y=type))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=x),colour="white")+
    geom_text(aes(label = round(x, 1)), size = 3.5) +
    scale_fill_gradient(low="white", high="steelblue")+
    ggtitle("2001-2021")+ 
    theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), panel.background = element_blank())+
    coord_fixed()
```

## domestic rates
```{r, echo=FALSE}
data<-Domestic_rate
colnames(data)<-c("district","type","x")

ggplot(data=data, aes(x=district, y=type))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=x),colour="white")+
    geom_text(aes(label = round(x, 2)), size = 3.5) +
    scale_fill_gradient(low="white", high="steelblue")+
    ggtitle("2001-2021")+ 
    theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), panel.background = element_blank())+
    coord_fixed()
```

notes for me: Assault is threat of violence. Battery is physical contact that causes bodily harm.\

# different types

## raw frequencies

```{r, echo=FALSE}
raw_frequency_ts<-trans(raw_frequency)
raw_frequency_ts[is.na(raw_frequency_ts)]<-0
corstars(raw_frequency_ts,removeTriangle="lower")
```

1-Homicide has not strong correlation with other types of crime. But in the first figure(raw frequencies heat map), it seems that district with more homicide has also more robbery, assault, and robbery, and vice versa. Why?\
2-The patterns of correlation matrix are similar using different data.\

## arrest reports

```{r, echo=FALSE}
arrest_report2<-subset(raw_frequency[which(raw_frequency$Arrest == TRUE),])
arrest_reports_ts<-trans(arrest_report2)
arrest_reports_ts[is.na(arrest_reports_ts)]<-0
```

```{r, echo=FALSE}
corstars(arrest_reports_ts,removeTriangle="lower")
```

## arrest arrest

```{r, echo=FALSE}
rate<-cbind(arrest_reports_ts,raw_frequency_ts)
rate[is.na(rate)]<-0
arrest_rates_ts<-arrest_reports_ts
arrest_rates_ts[,]<-NA
arrest_rates_ts[,1:4]<-round(rate[,1:4]/rate[,5:8],2)
arrest_rates_ts[is.na(arrest_rates_ts)]<-0
```

```{r, echo=FALSE}
corstars(arrest_rates_ts,removeTriangle="lower")
```

## domestic reports

```{r, echo=FALSE}
domestic_report2<-subset(raw_frequency[which(raw_frequency$Domestic == TRUE),])
domestic_reports_ts<-trans(domestic_report2)
```

```{r, echo=FALSE}
corstars(domestic_reports_ts,removeTriangle="lower")
```

## domestic arrest

```{r, echo=FALSE}
rate<-cbind(domestic_reports_ts,raw_frequency_ts)
rate[is.na(rate)]<-0
domestic_rates_ts<-domestic_reports_ts
domestic_rates_ts[,]<-NA
domestic_rates_ts[,1:4]<-round(rate[,1:4]/rate[,5:8],2)
domestic_rates_ts[is.na(domestic_rates_ts)]<-0
```

```{r, echo=FALSE}
corstars(domestic_rates_ts,removeTriangle="lower")
```
