---
title: "Bcp_freq"
author: "XuranZeng"
date: "9/14/2021"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=5, fig.pash='Figs/', echo = TRUE, warning=FALSE, message=FALSE)
```

## Update:
### 9/21
1. Time series charts: add moving average lines 
2. Heatmap of months and zones: calculate log, order by zones
3. Heatmap of weeks for each zone: add titles
4. Combine two files together
5. Answer questions in notebook.html: **insignificant mu**, residuals, non-stationary, ARCH/GARCH
6. Model at day level: **Surprisingly**, all zones satisfy ARIMA model(the residuals are independent, and there is no ARCH effect)
7. Latex workflow: see Latex_workflow.txt and Latex_workflow.png(or https://www.overleaf.com/project/614b69b13fd60a64aef35d3c)


```{r, echo=FALSE}
library(readr)
library(PerformanceAnalytics)
library(lubridate)
library(zoo)
library(xts)
library(ggplot2)
library(dplyr)
Bpc_freq<-read_csv("/project/graziul/data/bpc_freq.csv")
Bpc_freq$ts<-ymd_hm(unlist(Bpc_freq[,3]))
Bpc_freq<-Bpc_freq[,c(5,1,2,3,4)]
```


```{r}
#description(zone-days-start-end-files-hours of speech)
zone_list<-unique(Bpc_freq$zone)

des<-data.frame(zone=zone_list)
for (i in 1:length(zone_list)){
  des[i,"ndays"]<-nrow(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'date']))
  des[i,"start"]<-head(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'ts']),1)
  des[i,"end"]<-tail(unique(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),'ts']),1)
  des[i,"nfiles"]<-nrow(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),])
  des[i,"num_bpc"]<-sum(Bpc_freq[which(Bpc_freq$zone==zone_list[i]),"num_bpc"])
}
print(des)
```

```{r,echo=FALSE}
zone_1<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 1"),])
zone_10<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 10"),])
zone_11<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 11"),])
zone_12<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 12"),])
zone_13<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 13"),])
zone_2<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 2"),])
zone_3<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 3"),])
zone_4<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 4"),])
zone_5<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 5"),])
zone_6<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 6"),])
zone_8<-as.data.frame(Bpc_freq[which(Bpc_freq$zone=="Zone 8"),])
```

## Visualization
```{r,echo=FALSE}
#plot
sma<-stats::filter(ts(zone_1[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_1, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("Zone_1")

sma<-stats::filter(ts(zone_2[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_2, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_2")

sma<-stats::filter(ts(zone_3[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_3, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_3")

sma<-stats::filter(ts(zone_4[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_4, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_4")

sma<-stats::filter(ts(zone_5[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_5, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_5")

sma<-stats::filter(ts(zone_6[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_6, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_6")

sma<-stats::filter(ts(zone_8[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_8, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_8")

sma<-stats::filter(ts(zone_10[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_10, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_10")

sma<-stats::filter(ts(zone_11[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_11, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_11")

sma<-stats::filter(ts(zone_12[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_12, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_12")

sma<-stats::filter(ts(zone_13[,c(1,5)])/144,filter=c(rep(1,144)))
ggplot(data = zone_13, aes(x=ts, y=num_bpc)) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  ggtitle("zone_13")

```

```{r,echo=FALSE}
sum_by_freq<-function(data,freq){
  data %>%
    mutate(freq=freq(data$ts)) %>%
    group_by(freq) %>%
    summarise(sum_by_mon=sum(log(num_bpc)))
}

a1<-sum_by_freq(zone_1,month)
colnames(a1)<-c("month","zone_1")
a2<-sum_by_freq(zone_2,month)
colnames(a2)<-c("month","zone_2")
a3<-sum_by_freq(zone_3,month)
colnames(a3)<-c("month","zone_3")
a4<-sum_by_freq(zone_4,month)
colnames(a4)<-c("month","zone_4")
a5<-sum_by_freq(zone_5,month)
colnames(a5)<-c("month","zone_5")
a6<-sum_by_freq(zone_6,month)
colnames(a6)<-c("month","zone_6")
a8<-sum_by_freq(zone_8,month)
colnames(a8)<-c("month","zone_8")
a10<-sum_by_freq(zone_10,month)
colnames(a10)<-c("month","zone_10")
a11<-sum_by_freq(zone_11,month)
colnames(a11)<-c("month","zone_11")
a12<-sum_by_freq(zone_12,month)
colnames(a12)<-c("month","zone_12")
a13<-sum_by_freq(zone_13,month)
colnames(a13)<-c("month","zone_13")

b<-cbind(a1, a2, a4,  a8, a10, a11, a12, a13)[,c(1,2,4,6,8,10,12,14,16)]
c<-merge(b, a3, by = 'month', all=T)
d<-merge(c, a5, by = 'month', all=T)
e<-merge(d, a6, by = 'month', all=T)
g<-e[,c(1,2,3,10,4,11,12,5,6,7,8,9)]
library(reshape2)
f<-melt(g, id="month")

mymonths<-c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul","Aug","Sep","Oct","Nov","Dec")
month.name<-sort(unique(f$month))
f$month2<-factor(f$month, levels=month.name, labels=mymonths)

ggplot(data=f, aes(x=month2, y=variable))+
  theme_bw(base_family = "STKaiti")+
  geom_tile(aes(fill=value),colour="white")+
  scale_fill_gradient(low="white", high="black")+
  ggtitle("month-zone(log)")+
  xlab("month")+
  ylab("zones")



```


```{r,echo=FALSE, fig.width=12, fig.height=3}
plot_hm<-function(data){
  data$week<-week(data$ts)
  data$weekdays<-weekdays(data$ts)
  zone_hm<-ggplot(data=data, aes(x=week, y=weekdays))+
    theme_bw(base_family = "STKaiti")+
    geom_tile(aes(fill=num_bpc),colour="white")+
    scale_fill_gradient(low="white", high="black")
  return(zone_hm)
}

plot_hm(zone_1[,c(1,5)])+ggtitle("zone_1")
plot_hm(zone_2[,c(1,5)])+ggtitle("zone_2")
plot_hm(zone_3[,c(1,5)])+ggtitle("zone_3")
plot_hm(zone_4[,c(1,5)])+ggtitle("zone_4")
plot_hm(zone_5[,c(1,5)])+ggtitle("zone_5")
plot_hm(zone_6[,c(1,5)])+ggtitle("zone_6")
plot_hm(zone_8[,c(1,5)])+ggtitle("zone_8")
plot_hm(zone_10[,c(1,5)])+ggtitle("zone_10")
plot_hm(zone_11[,c(1,5)])+ggtitle("zone_11")
plot_hm(zone_12[,c(1,5)])+ggtitle("zone_12")
plot_hm(zone_13[,c(1,5)])+ggtitle("zone_13")
```

## modeling and prediction
```{r, echo=FALSE}
#library(shiny)
library(readr)
library(lubridate)
library(zoo)
library(xts)
library(ggplot2)
```


```{r}
Bpc_freq<-read_csv("/project/graziul/data/bpc_freq.csv")
Bpc_freq$ts<-ymd_hm(unlist(Bpc_freq$file))
Bpc_freq<-Bpc_freq[,c('ts','zone','num_bpc')]
```

```{r}
## Input: number of zone(1-13);raw data of BPC
## Output: dataframe of zone Bpc(ts;zone;num_bpc)
## Functionality: extract data of the zone that we want to analyze
extract_zone = function(z, data){
  zone_name <-paste("Zone",z)
  cat("Model and predict data from:",zone_name,"\n")
  zone<-as.data.frame(Bpc_freq[which(Bpc_freq$zone==zone_name),])
}
```

```{r}
## Input: zone dataframe(ts, num_bpc)
## Output: dataframe of zone daily bpc(date;num_bpc)
## Functionality: calculate number of bpc per day in the zone
sum_by_day = function(zone){
  date_1<-unique(as.Date(zone$ts))
  sum_by_day<-data.frame(date=date_1)
  for (i in 1:length(date_1)){
    sum_by_day[i,"num_bpc"]<-sum(Bpc_freq[which(as.Date(zone$ts)==date_1[i]),"num_bpc"]
    )
  }
  zone<-sum_by_day
}
```

```{r}
## Input: zone dataframe(ts, num_bpc)
## Output: ARIMA/GARCH model
## Functionality: conduct stationary test, set up ARIMA model, conduct residuals test, set up GARCH model
MP = function(zone){
  # plot time series
  ggplot(data = zone, aes(x=date, y=num_bpc)) +  
    geom_line()+
    ggtitle("Zone_1")
  
  # plot ACF, PACF 
  par(mfrow=c(1,2))
  acf(zone$num_bpc, lag.max = 20, main="ACF(20)")
  pacf(zone$num_bpc, lag.max = 20, main="PACF(20)")
  
  # stationary test
  cat("Conduct stationary test:","\n")
  library(urca)
  
  print(summary(ur.kpss(zone$num_bpc)))
  
  teststata = ur.kpss(zone$num_bpc) @teststat
  cval = ur.kpss(zone$num_bpc) @cval[4]
  
  if (teststata > cval) {
    cat("Test statistic is larger than critical value:","\n","\n")
    cat("Timeseries are not stationary","\n","\n")
    cat("Use diff to transfer data into stationary timeseries","\n","\n")
    
    # transfer nonstationary ts to stationary
    tss<-ts(zone$num_bpc,freq=length(zone$num_bpc),start=1)
    library(forecast)
    cat("number of diff:",ndiffs(tss),"\n","\n")
    ts_adj<-diff(tss,diff=ndiffs(tss))
    
    #check again
    
    cat("Conduct Stationary Test:","\n")
    print(summary(ur.kpss(ts_adj)))
    
    teststata2 = ur.kpss(ts_adj) @teststat
    cval2 = ur.kpss(ts_adj) @cval[4]
    
    if(teststata2 > cval2){
      cat("Test statistic is larger than critical value:","\n","\n")
      cat("Adjusted timeseries are not stationary","\n","\n")
      return(message("Adjusted timeseries are not stationary"))
    } else{
      
      cat("T-statistic is smaller than critical value:","\n","\n")
      cat("Adjusted timeseries are stationary","\n","\n")
      cat("Set up ARIMA model","\n","\n")
    }
    
    
  } else {
    cat("T-statistic is smaller than critical value:","\n","\n")
    cat("Timeseries are stationary","\n","\n")
    cat("Set up ARIMA model","\n","\n")
    ts_adj<-(zone$num_bpc)
  }
  
  # ARIMA
  fit<-auto.arima(ts_adj,seasonal = FALSE)
  print(summary(fit))
  
  # Check Residual
  cat("\n","Conduct residuals check:","\n","\n")
  
  print(Box.test(resid(fit),type="Ljung",lag=20))
  
  teststata3 = Box.test(resid(fit),type="Ljung",lag=20)$p.value
  cval3 = 0.05 ##
  
  if(teststata3 < cval3){
    cat("P-value is small:","\n","\n")
    cat("Reject null hypothesis: residuals are independent.","\n","\n")
    cat("So residuals are not white-noise, and this ARIMA model is flawed.","\n","\n")
    cat("Set up ARCH model","\n","\n")
    
    # Engle ARCH LM test
    # Null hypothesis: no ARCH effects
    
    cat("Conduct Arch-LM test:","\n","\n")
    library(FinTS)
    
    print(ArchTest(resid(fit)))
    
    teststata4 = ArchTest(resid(fit))$p.value
    cval4 = 0.05 ##
    
    if(teststata4<cval4){
      cat("P-value is small:","\n","\n")
      cat("Reject null hypothesis: no ARCH effects ","\n","\n")
      cat("ARCH effects exist","\n","\n")
      cat("Set up ARCH/GARCH model","\n","\n")
      library(rugarch)
      spec = ugarchspec()
      def.fit=ugarchfit(spec=spec, data=ts_adj)
      print(def.fit)
      cat("Residuals nomorality test: ","\n","\n")
      plot(def.fit,which=8)
      plot(def.fit,which=9)
      cat("Residuals correlation test: ","\n","\n")
      plot(def.fit,which=11)
      cat("Forecast: ","\n","\n")       
      ugarchforecast(def.fit, n.ahead=7, data=ts_adjust)
      
      
    } else{
      return(message("no suitable model"))
    }
    
    
  } else {
    cat("P-value is larger than 0.05:","\n","\n")
    print("Residuals are white-noise")
    print("This ARIMA model is suitable")
    fit<-auto.arima(ts_adj,seasonal = FALSE)
    
    plot(fit %>% forecast(h=10) %>% autoplot(include=80))
  }
  
}
```

```{r}
zone_i<-extract_zone(13, Bpc_freq)
```

```{r}
zone_i_day<-sum_by_day(zone_i)
```

#### model and predict with daily data
```{r}
MP(zone_i_day)
```

#### model and predict with raw data (files)
```{r}
MP(zone_i)
```
