---
title: "reported-crimes"
author: "XuranZeng"
date: "9/26/2021"
output: 
  html_document: 
    toc: yes
    toc_float: true 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.pash='Figs/', echo = TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library(readr)
library(PerformanceAnalytics)
library(lubridate)
library(zoo)
library(xts)
library(ggplot2)
library(dplyr)
library(knitr)
library(corrplot)
library(forecast)
```

# Reported crimes
## types of reported crimes within each district
```{r, echo=FALSE}
# time: entire sample
# log(num_reported_crime)
crimes_data<-read_csv("/home/xuranzeng/crimes_data.csv",)
crimes_data_sample<-crimes_data[,c('Date','Primary Type','District')]
a<-aggregate(crimes_data_sample$`Primary Type`,by=list(district=crimes_data_sample$District, type=crimes_data_sample$`Primary Type`),length)


ggplot(data=a, aes(x=district, y=type))+
  theme_bw(base_family = "STKaiti")+
  geom_tile(aes(fill=log(x)),colour="white")+
  scale_fill_gradient(low="white", high="black")+
  ggtitle("2001-2021")
```
Difference between each district is not obvious. See last 5 years(2018-2021)

```{r, echo=FALSE}
crimes_data$year<-year(as.Date(unlist(crimes_data$Date),"%m/%d/%Y"))
crimes_data_2018_2021<-as.data.frame(crimes_data[which(crimes_data$year>2017),])
crimes_data_sample<-crimes_data_2018_2021
a<-aggregate(crimes_data_sample$`Primary Type`,by=list(district=crimes_data_sample$District, type=crimes_data_sample$`Primary Type`),length)


ggplot(data=a, aes(x=district, y=type))+
  theme_bw(base_family = "STKaiti")+
  geom_tile(aes(fill=log(x)),colour="white")+
  scale_fill_gradient(low="white", high="black")+
  ggtitle("2018-2021")
```
1-Narcotics: districts with most reported-narcotics are 10, 11, 15 and 25, which are zone 12 and zone 10 (but you told me before that zone which most drug is zone 2-district19?)\
2-Weapon Violation: districts with most reported-weapon violation are 10, 11, 6, 7, 9 and 12 which are zone 10, zone 6, and zone 13

## focus on district 10

### raw frequencies

#### correlation between different types (2001-2021, Pearson correlation)
```{r, echo=FALSE}
crimes_data_10<-as.data.frame(crimes_data[which(crimes_data$District=='010'),])
```

```{r, echo=FALSE}
a<-aggregate(crimes_data_10$`Primary Type`,by=list(year=crimes_data_10$year, type=crimes_data_10$`Primary Type`),length)

type_ts<-as.data.frame(unique(a$year))
colnames(type_ts)<-"year"
for (i in 1:length(unique(a$type))){
  b<-subset(a[which(a$type==unique(a$type)[i]),])
  type_ts<-merge(type_ts,b[,c(1,3)],by="year",all=TRUE)
  colnames(type_ts)[(i+1)]<-unique(a$type)[i]
}

b<-type_ts
rownames(b)<-b$year
b<-b[,-1]
b[is.na(b)]<-0

#png(file="corr_plot.png",width=3000,height=3000)
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor(b), method="color", col=col(200),
         order="hclust",
         addCoef.col = "black",number.cex = 0.5, #添加相关系数
         tl.col="black", tl.srt=45,tl.cex=0.8 #修改字体
         )
```

### correlation higher than 0.9
```{r,echo=FALSE}

a<-as.matrix(cor(b))

df<-data.frame(idrow=rep(rownames(a),ncol(a)),
    idcol=rep(colnames(a),each=nrow(a)),
    value=as.vector(a))

rm=which(df$value==1)
df=df[-rm,]
c<-df[df$value>=0.9,]
d<-c[order(c$value,decreasing = T),]
e<-d[!duplicated(d$value),]
kable(e)
```

## ARIMA-GARCH model (use weapon and narcotics data, ARIMA-GARCH model defined before)(which data to use??)
```{r,echo=FALSE}
crimes_data_10<-as.data.frame(crimes_data[which(crimes_data$District=='010'),])
crimes_data_10$day<-date(as.Date(unlist(crimes_data_10$Date),"%m/%d/%Y"))
crimes_data_10_day<-crimes_data_10[,c(11, 3,8,9)]

a<-aggregate(crimes_data_10_day$`Primary Type`,by=list(day=crimes_data_10_day$day, type=crimes_data_10_day$`Primary Type`),length)

type_ts<-as.data.frame(unique(a$day))
colnames(type_ts)<-"day"
for (i in 1:length(unique(a$type))){
  b<-subset(a[which(a$type==unique(a$type)[i]),])
  type_ts<-merge(type_ts,b[,c(1,3)],by="day",all=TRUE)
  colnames(type_ts)[(i+1)]<-unique(a$type)[i]
}

b<-type_ts
rownames(b)<-b$day
b<-b[,-1]
b[is.na(b)]<-0
```

```{r, echo=FALSE}
weapon_narcotics<-b[,c("NARCOTICS" , "WEAPONS VIOLATION")]
weapon_narcotics$date<-rownames(weapon_narcotics)
narcotics<-weapon_narcotics[,c(3,1)]
weapon<-weapon_narcotics[,c(3,2)]

```


```{r,echo=FALSE}

MP = function(zone){
  
  colnames(zone)<-c("date","num_bpc")
  
  
  # plot time series
  ggplot(data = zone, aes(x=as.Date(date), y=num_bpc)) +  
    geom_line()+
    ggtitle("Zone_1")
  
  # plot ACF, PACF 
  par(mfrow=c(1,2))
  acf(zone$num_bpc, lag.max = 20, main="ACF(20)")
  pacf(zone$num_bpc, lag.max = 20, main="PACF(20)")
  
  # stationary test
  cat("Conduct stationary test:","\n")
  library(urca)
  
  print(summary(ur.kpss(zone$num_bpc)))
  
  teststata = ur.kpss(zone$num_bpc) @teststat
  cval = ur.kpss(zone$num_bpc) @cval[4]
  
  if (teststata > cval) {
    cat("Test statistic is larger than critical value:","\n","\n")
    cat("Timeseries are not stationary","\n","\n")
    cat("Use diff to transfer data into stationary timeseries","\n","\n")
    
    # transfer nonstationary ts to stationary
    tss<-ts(zone$num_bpc,freq=length(zone$num_bpc),start=1)
    library(forecast)
    cat("number of diff:",ndiffs(tss),"\n","\n")
    ts_adj<-diff(tss,diff=ndiffs(tss))
    
    #check again
    
    cat("Conduct Stationary Test:","\n")
    print(summary(ur.kpss(ts_adj)))
    
    teststata2 = ur.kpss(ts_adj) @teststat
    cval2 = ur.kpss(ts_adj) @cval[4]
    
    if(teststata2 > cval2){
      cat("Test statistic is larger than critical value:","\n","\n")
      cat("Adjusted timeseries are not stationary","\n","\n")
      return(message("Adjusted timeseries are not stationary"))
    } else{
      
      cat("T-statistic is smaller than critical value:","\n","\n")
      cat("Adjusted timeseries are stationary","\n","\n")
      cat("Set up ARIMA model","\n","\n")
    }
    
    
  } else {
    cat("T-statistic is smaller than critical value:","\n","\n")
    cat("Timeseries are stationary","\n","\n")
    cat("Set up ARIMA model","\n","\n")
    ts_adj<-(zone$num_bpc)
  }
  
  # ARIMA
  fit<-auto.arima(ts_adj,seasonal = FALSE)
  print(summary(fit))
  
  # Check Residual
  cat("\n","Conduct residuals check:","\n","\n")
  
  print(Box.test(resid(fit),type="Ljung",lag=20))
  
  teststata3 = Box.test(resid(fit),type="Ljung",lag=20)$p.value
  cval3 = 0.05 #
  
  if(teststata3 < cval3){
    cat("P-value is small:","\n","\n")
    cat("Reject null hypothesis: residuals are independent.","\n","\n")
    cat("So residuals are not white-noise, and this ARIMA model is flawed.","\n","\n")
    cat("Set up ARCH model","\n","\n")
    
    # Engle ARCH LM test
    # Null hypothesis: no ARCH effects
    
    cat("Conduct Arch-LM test:","\n","\n")
    library(FinTS)
    
    print(ArchTest(resid(fit)))
    
    teststata4 = ArchTest(resid(fit))$p.value
    cval4 = 0.05 #
    
    if(teststata4<cval4){
      cat("P-value is small:","\n","\n")
      cat("Reject null hypothesis: no ARCH effects ","\n","\n")
      cat("ARCH effects exist","\n","\n")
      cat("Set up ARCH/GARCH model","\n","\n")
      
      library(rugarch)
      spec = ugarchspec()
      def.fit=ugarchfit(spec=spec, data=ts_adj)
      print(def.fit)
      cat("Forecast: ","\n","\n")       
      ugarchforecast(def.fit, n.ahead=7, data=ts_adjust)
      
      
    } else{
      return(message("no suitable model"))
    }
    
    
  } else {
    cat("P-value is larger than 0.05:","\n","\n")
    print("Residuals are white-noise")
    print("This ARIMA model is suitable")
    fit<-auto.arima(ts_adj,seasonal = FALSE)
    
    plot(fit %>% forecast(h=10) %>% autoplot(include=80))
  }
  
  
  
}
```

### narcotics ARIMA-GARCH model

```{r, echo=FALSE}
sma<-stats::filter(ts(narcotics)/144,filter=c(rep(1,144)))
ggplot(data = weapon, aes(x=as.Date(narcotics[,1]), y=narcotics[,2])) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  labs(x="date",y="num",title="narcotics")
```

```{r}
MP(narcotics)
narcotics_st<-ts_adj
```

### weapon ARIMA-GARCH model
```{r, echo=FALSE}
sma<-stats::filter(ts(weapon[,c(1,2)])/144,filter=c(rep(1,144)))
ggplot(data = weapon, aes(x=as.Date(weapon[,1]), y=weapon[,2])) +  
  geom_line()+
  geom_line(aes(y=sma[,2]),color="red")+
  labs(x="date",y="num",title="weapon")
```

```{r}
MP(weapon)
```

### weapon-narcotics DCC model

```{r, echo=FALSE}
stationary=function(zone){
  colnames(zone)<-c("date","num_bpc")
  
  # stationary test
  cat("Conduct stationary test:","\n")
  library(urca)
  
  print(summary(ur.kpss(zone$num_bpc)))
  
  teststata = ur.kpss(zone$num_bpc) @teststat
  cval = ur.kpss(zone$num_bpc) @cval[4]
  
  if (teststata > cval) {
    cat("Test statistic is larger than critical value:","\n","\n")
    cat("Timeseries are not stationary","\n","\n")
    cat("Use diff to transfer data into stationary timeseries","\n","\n")
    
    # transfer nonstationary ts to stationary
    tss<-ts(zone$num_bpc,freq=length(zone$num_bpc),start=1)
    library(forecast)
    cat("number of diff:",ndiffs(tss),"\n","\n")
    ts_adj<-diff(tss,diff=ndiffs(tss))
    cat("adjusted time-series is stationary","\n","\n")
  }else{
    
    cat("T-statistic is smaller than critical value:","\n","\n")
    cat("Adjusted timeseries are stationary","\n","\n")
  }
  return(ts_adj)
}
```

```{r,echo=FALSE}
weapon_narcotics<-b[,c("NARCOTICS" , "WEAPONS VIOLATION")]
weapon_narcotics$date<-rownames(weapon_narcotics)

narcotics_st<-stationary(narcotics)
weapon_st<-stationary(weapon)
weapon_narcotics_st<-as.data.frame(cbind(narcotics_st,weapon_st))
date<-rownames(weapon_narcotics)[-1]
weapon_narcotics_st$date<-date
weapon_narcotics_st<-xts(weapon_narcotics_st[,1:2],ymd(weapon_narcotics_st[,3]))

sma<-stats::filter(ts(narcotics)/144,filter=c(rep(1,144)))
plot(sma[,2])

sma1<-stats::filter(ts(weapon)/140,filter=c(rep(1,144)))
plot(sma1[,2])
```
