---
title: "windows"
author: "XuranZeng"
date: "11/11/2021"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=3, fig.pash='Figs/', echo = TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE}
library(readr)
library(lubridate)
library(ggplot2)
library(dplyr)
library(knitr)
library(RcppRoll)
```



# Data / Function description
path: /project/graziul/ra/xuranzeng/windows

raw_crimes_beat_transfer.csv: time series of # daily reported crimes each beat

raw_crimes_beat_roll_sum_30.csv: 30-day rolling window of # daily reported crimes each beat

raw_crimes_beat_roll_vol_30.csv: 30-day rolling window of daily reported crimes volatility each beat

raw_crimes_beat_roll_sum_7.csv: 7-day rolling window of # daily reported crimes each beat

raw_crimes_beat_roll_vol_7.csv: 7-day rolling window of daily reported crimes volatility each beat

roll_30_summary.csv: max-sum-window, max-num, max-volatility-window, max-volatility of each beat (30 days)

roll_7_summary.csv: max-sum-window, max-num, max-volatility-window, max-volatility of each beat (7 days)


homicide_crimes_beat_transfer.csv: time series of # daily reported homicides each beat

homicide_crimes_beat_roll_sum_30.csv: 30-day rolling window of # daily reported homicide each beat

homicide_crimes_beat_roll_vol_30.csv: 30-day rolling window of daily reported homicide volatility each beat

homicide_crimes_beat_roll_sum_7.csv: 7-day rolling window of # daily reported homicide each beat

homicide_crimes_beat_roll_vol_7.csv: 7-day rolling window of daily reported homicide volatility each beat

homicide_roll_30_summary.csv: max-sum-window, max-num, max-volatility-window, max-volatility of each beat (30 days)

homicide_roll_7_summary.csv: max-sum-window, max-num, max-volatility-window, max-volatility of each beat (7 days)



roll_sum_i: input ts data and length of window (30 / 7), output rolling sum

roll_vol_i: input ts data and length of window (30 / 7), output rolling standard deviation

roll_summary: input rolling sum data and length of window (30 / 7), output summary of rolling sum (max-window, max-num, min-window, min-num of each beat)

plot_max: input rolling sum data and the beat, output ts plot,max sum window, max # reports of that beat, max volatility window, max volatility of that beat

```{r, echo=FALSE}
roll_sum_i<-function(data, i){
  roll_sum_30<-as.data.frame(data[i:nrow(data),'Date'])
  rownames(roll_sum_30)<-roll_sum_30[,1]
  raw_crimes2<-data[,3:ncol(data)]
  for (j in 1:ncol(raw_crimes2)){
  roll_sum_30[,j]<-roll_sum(unlist(raw_crimes2[,j]),n=i)
  #cat("merging:",i,'\n')
  }
  colnames(roll_sum_30)<-colnames(raw_crimes2)
  return(roll_sum_30)
}
```

```{r, echo=FALSE}
roll_vol_i<-function(data, i){
  roll_vol_30<-as.data.frame(data[i:nrow(data),'Date'])
  rownames(roll_vol_30)<-roll_vol_30[,1]
  raw_crimes2<-data[,3:ncol(data)]
  for (j in 1:ncol(raw_crimes2)){
    roll_vol_30[,j]<-roll_sd(unlist(raw_crimes2[,j]),n=i)
  }
  colnames(roll_vol_30)<-colnames(raw_crimes2)
  return(roll_vol_30)
}
```

```{r, echo=FALSE}
roll_summary<-function(datasum,datavol,interval){
  roll_sum_30_summary<-as.data.frame(colnames(datasum))
  
  max_sum_window<-NA
  max_num<-NA
  for (i in 1:ncol(datasum)){
    beat<-colnames(datasum)[i]
    max<-which.max(datasum[,beat])
    max_sum_window[i]<-paste(rownames(datasum)[max-interval],rownames(datasum)[max],sep = '-')
    max_num[i]<-datasum[max,beat]
  }

  
  roll_sum_30_summary$max_sum_window<-max_sum_window
  roll_sum_30_summary$max_num<-max_num
  
  max_vol_window<-NA
  max_vol<-NA
  for (i in 1:ncol(datavol)){
    beat<-colnames(datavol)[i]
    max<-which.max(datavol[,beat])
    max_vol_window[i]<-paste(rownames(datavol)[max-interval],rownames(datavol)[max],sep = '-')
    max_vol[i]<-datavol[max,beat]
  }

  
  roll_sum_30_summary$max_vol_window<-max_vol_window
  roll_sum_30_summary$max_vol<-max_vol
  
  return(roll_sum_30_summary)
  
}
```

```{r, echo=FALSE}
plot_max<-function(datasum,datavol,i){
    beat<-colnames(datasum)[i]
    max_sum<-which.max(datasum[,beat])
    
    max_vol<-which.max(datavol[,beat])
    max_vol0<-which.max(datavol[,beat])-i
    
    max_x0<-as.Date(rownames(datavol)[max_vol])
    max_x1<-as.Date(rownames(datavol)[max_vol0])
    
    p<-ggplot(data=datasum,aes(x=as.Date(rownames(datasum)),y=datasum[,beat],xlab="year",ylab=beat))+
      geom_line()+
      geom_point(data = roll_sum_30,aes(x=as.Date(rownames(datasum)[max_sum]),y=datasum[max_sum,beat]), color="red", size=3)+
      geom_rect(xmin=max_x0, xmax=max_x1, ymin=-Inf, ymax=Inf, color="red", alpha=0.5)
    cat("highest reported crimes for beat",beat,":",rownames(datasum)[max_sum-30],'-',rownames(datasum)[max_sum],'\n')
    cat("# reported crimes:",datasum[max_sum,beat],'\n')
    cat("highest volatility for beat",beat,":",rownames(datasum)[max_vol0],'-',rownames(datasum)[max_vol],'\n')
    cat("# reported crimes:",datavol[max_vol,beat],'\n')
    return(p)
}

```



# 30 days + all crimes

```{r, echo=FALSE}
raw_crimes2<-read_csv("/home/xuranzeng/project/data/raw_crimes_beat_transfer.csv",)
rownames(raw_crimes2)<-raw_crimes2$Date
```

```{r}
roll_sum_30<-roll_sum_i(raw_crimes2,30)
roll_vol_30<-roll_vol_i(raw_crimes2,30)

#write.csv(roll_vol_30,"/home/xuranzeng/project/data/raw_crimes_beat_roll_vol_30.csv")
```



```{r}
plot_max(roll_sum_30,roll_vol_30,1)

plot_max(roll_sum_30,roll_vol_30,5)
```

```{r}
roll_sum_30_summary<-roll_summary(roll_sum_30,roll_vol_30,30)
head(roll_sum_30_summary)
#write.csv(roll_sum_30_summary,"/home/xuranzeng/project/data/roll_sum_30_summary.csv")
```


# 7 days + all crimes
```{r, echo=FALSE}
raw_crimes2<-read_csv("/home/xuranzeng/project/data/raw_crimes_beat_transfer.csv",)
rownames(raw_crimes2)<-raw_crimes2$Date
```

```{r}
roll_sum_7<-roll_sum_i(raw_crimes2,7)
roll_vol_7<-roll_vol_i(raw_crimes2,7)
#write.csv(roll_sum_7,"/home/xuranzeng/project/data/raw_crimes_beat_roll_sum_7.csv")
#write.csv(roll_vol_7,"/home/xuranzeng/project/data/raw_crimes_beat_roll_vol_7.csv")
```


```{r}
plot_max(roll_sum_7,roll_vol_7,1)

plot_max(roll_sum_7,roll_vol_7,5)
```

```{r}
roll_sum_7_summary<-roll_summary(roll_sum_7,roll_vol_7,7)
head(roll_sum_7_summary)
#write.csv(roll_sum_7_summary,"/home/xuranzeng/project/data/roll_sum_7_summary.csv")
```






# 30 days + homicide crimes

```{r, echo=FALSE}
raw_crimes2<-read_csv("/home/xuranzeng/project/data/homicide_crimes_beat_transfer.csv",)
rownames(raw_crimes2)<-raw_crimes2$Date
```


```{r}
roll_sum_30<-roll_sum_i(raw_crimes2,30)
roll_vol_30<-roll_vol_i(raw_crimes2,30)
#write.csv(roll_sum_30,"/home/xuranzeng/project/data/homicide_roll_sum_30.csv")
#write.csv(roll_vol_30,"/home/xuranzeng/project/data/homicide_roll_vol_30.csv")
```


```{r}
plot_max(roll_sum_30,roll_vol_30,1)

plot_max(roll_sum_30,roll_vol_30,5)

```

```{r}
roll_sum_30_summary<-roll_summary(roll_sum_30,roll_vol_30,30)
head(roll_sum_30_summary)
#write.csv(roll_sum_30_summary,"/home/xuranzeng/project/data/homicide_roll_sum_30_summary.csv")
```



# 7 days + homicide crimes

```{r, echo=FALSE}
raw_crimes2<-read_csv("/home/xuranzeng/project/data/homicide_crimes_beat_transfer.csv",)
rownames(raw_crimes2)<-raw_crimes2$Date
```


```{r}
roll_sum_7<-roll_sum_i(raw_crimes2,7)
roll_vol_7<-roll_vol_i(raw_crimes2,7)
#write.csv(roll_sum_7,"/home/xuranzeng/project/data/homicide_roll_sum_7.csv")
#write.csv(roll_vol_7,"/home/xuranzeng/project/data/homicide_roll_vol_7.csv")
```


```{r}

plot_max(roll_sum_7,roll_vol_7,1)

plot_max(roll_sum_7,roll_vol_7,5)

```

```{r}
roll_sum_7_summary<-roll_summary(roll_sum_7,roll_vol_7,7)
head(roll_sum_7_summary)
#write.csv(roll_sum_30_summary,"/home/xuranzeng/project/data/homicide_roll_sum_7_summary.csv")
```

